---
output:
  pdf_document: default
  html_document: default
header-includes: 
    - \usepackage{amsthm}
    - \usepackage{xcolor}
documentclass: article
<!---output: beamer_presentation--->
---

```{r global_options, include=FALSE}
knitr::opts_chunk$set(error=TRUE,        # Keep compiling upon error
                      collapse=TRUE,     # collapse by default
                      echo=TRUE,         # echo code by default
                      comment = "#>",    # change comment character
                      fig.width = 10,     # set figure width
                      out.width = "100%", # set width of displayed images
                      warning=TRUE,      # show R warnings
                      message=FALSE)     # show R messages

packageTest<- function(x)  {
    if (!require(x,character.only = TRUE))  {
      install.packages(x,dep=TRUE)
      if(!require(x,character.only = TRUE)) stop("Package not found")
    }
}

options(warn=-1)
```


<!--- Solution Region --->
<style>
#solution {
  background-color: #8FBC8F;
  border-style: solid;
  border-color: blue;
  margin-left: 20px;
  margin-bottom: 15px;
  padding: 5px;
}
</style>



<!---**Sommersemester 2019 |Studiengang Data Science | Hochschule Darmstadt **--->




\theoremstyle{break}
\newtheorem{auf}{Aufgabe}

\newcommand{\R}{{\sffamily R} }

\begin{centering}
%\vspace{-2 cm}
\Huge
{\bf Uebung 1}\\
\Large
Computational Statistics\\
\normalsize
Sommersemester 2019\\
April 15, 2019\\
J. Groos (FBMN, h\_da)\\
\end{centering}


\hrulefill

**Name:**

\hrulefill


## A 1 
###a)

```{r}
summe=0
for (i in 1:1000){
  summe=summe+rnorm(500,0,1)
}
meanssim <- summe/1000
```
BLABLABLA

## A 1 
###b)
```{r}
packageTest('boot')
bootdata <- rnorm(500,0,1)
bootfunc <- function(x,d) {
  x[d]
}
boot <- boot(bootdata, bootfunc, R = 1000)
boot <- boot$t
meanboot <- colMeans(boot)

par(mfrow=c(2,2))
hist(meanboot)
hist(meanssim)
boxplot(meanboot)
boxplot(meanssim)
```
Hier k??nnte ihre Interpretation stehen:

## A 1 
### c)
```{r}

```
BLABLABLA 

